Classical mechanics as the high-entropy limit \\ of quantum mechanics

### 2025-11-27 Articles/2024-ClassicalLimit/classicalLimitArticle.tex
ClassicalLimit: responding to reviewers comments

In both classical and quantum mechanics, Gaussian states maximize entropy for a single independent degree of freedom at a fixed uncertainty or, equivalently, minimize uncertainty at fixed entropy. This means that, if we fix the entropy $S$, we will have an uncertainty relationship~\cite{Carcassi:2022bpm}
\begin{equation}
    \Delta x \Delta p \geq \Sigma(S).
\end{equation}
The specific value of the uncertainty $\Sigma$ will depend on the entropy and on whether we are using classical or quantum mechanics, though the relationship will always be saturated by Gaussian states with no correlation between $x$ and $p$.

@@

Mathematically, the trace distance $T(\rho,\sigma)$ between two mixed states $\rho$ and $\sigma$ is contractive under a completely positive trace-preserving (CPTP) map $M$. That is, $T(M(\rho),M(\sigma)) \leq T(\rho,\sigma)$~\cite{nielsen2010quantum}. In the finite-dimensional case, we can have a CPTP map that increases the entropy of all states except that of the maximally mixed state, which is a fixed point.\footnote{This is a particular instance of mixing/relaxing ergodic quantum channels where the fixed point is the maximally mixed state~\cite{Burgarth2012ErgodicAM}.}  Under such a map, all pure states are mapped to mixed states, orthogonal states are mapped to non-orthogonal states and the map is strictly contractive. In section~\ref{sec:high_entropy_limit}, when we construct the high-entropy limit, the map that results will follow this intuition in the infinite-dimensional case, with the only difference that there is no maximally mixed state that does not change.\footnote{In the infinite-dimensional case, one could have infinite-dimensional subspaces that remain orthogonal while increasing the entropy of all its elements. This corresponds, for example, to the case where there are conserved quantities. Note that in the map we construct in section 4, the expectation of all polynomials of position and momentum changes, and therefore no function of position and momentum is a conserved quantity. }  If we call $\mathcal{G}$ the space of all mixtures of Gaussian states, the states with a non-negative Wigner function, given an arbitrary mixed state $\rho$, we will find a state $\sigma_{\rho} \in \mathcal{G}$ that is closest to $\rho$. As we apply our entropy-increasing map, the entropy of $\rho$ increases and $\sigma_{\rho}$ will get closer to $\rho$. In this sense the states will ``look classical.''

@@

The failure of classical statistical mechanics to predict the black-body radiation spectrum was one of the key drivers for the development of quantum theory. The spectrum predicted by classical mechanics is given by the Rayleigh–Jeans law,
\begin{equation}
    \frac{2 \nu^2 k_\text{B} T}{c^2} = \frac{2 \nu^2}{c^2 \beta},
\end{equation}
where $\beta = \frac{1}{k_\text{B} T}$. The one predicted by quantum mechanics is given by Planck's law,
\begin{equation}
    \frac{ 2 h \nu^3}{c^2} \frac 1{\exp\left(\frac{h\nu}{k_\mathrm B T}\right) - 1} = \frac{ 2 h \nu^3}{c^2} \frac 1{e^{h \beta \nu} - 1}.
\end{equation}
It is well known that the two agree for small values of $\nu$ since $e^x \simeq 1 + x + O(x^2)$ for $x\ll 1$.
\begin{equation}
    \frac{ 2 h \nu^3}{c^2} \frac 1{e^{h \beta \nu} - 1} = \frac{ 2 h \nu^3}{c^2} \frac 1{1 + h \beta \nu + O\left(\nu^2\right) - 1} \simeq \frac{2 \nu^2}{c^2 \beta}.
\end{equation}

@@

Having given qualitative reasons for the limit, and having seen how, in specific cases, standard arguments can be reinterpreted consistently with our view, we now develop the limit as a direct consequence of entropy increase. Since the maximum entropy attainable by a quantum system is the logarithm of the dimension of the corresponding Hilbert space~\cite{nielsen2010quantum}, the high-entropy limit exists only for infinite-dimensional spaces. This explains why spin, which lives in a finite-dimensional space, is an intrinsically quantum property. Therefore we are going to concentrate on the case of a single degree of freedom identified by position and momentum. The case of multiple degrees of freedom can be recovered by increasing the entropy of all DOFs at the same time, that is, by increasing the entropy of each DOF independently, without introducing correlations.

@@

For a pure stretching map, we can provide a more specific characterization. Note, in fact, that a distribution with compact support is always fully characterized by all its central moments, that is, the expectations for all polynomials of position and momentum. Therefore, once we know how the central moments transform through the map, we know how all distributions with compact support transform and therefore we fully characterize the map. This means that $T$ is a pure stretching map if and only if
\begin{equation}
    \langle T(x^np^m) \rangle = (\sqrt{\lambda})^{(n+m)} \langle x^n p^m \rangle.
\end{equation}

@@

If pure quantum stretching maps $T_Q$ exist, they must be CPTP maps as they must transform mixed states into mixed states. Moreover, since they have to increase entropy for all states, they must be describing an open quantum system. We thus show that pure stretching maps can be expressed as the solution of a master equation in Lindblad form and the Heisenberg picture. We start with
\begin{equation}
	\frac{d}{d t} X=\frac{i}{\hbar}[H,X]+\sum_i \gamma_i \left(L_i^\dagger X L_i-\frac{1}{2}\left\{L_i^\dagger L_i,X\right\}\right)
\end{equation}
where $X$ is an operator, $L_i$ are the jump operators and $\gamma_i$ are positive parameters. To define $T_Q$ for a single DOF we set $\gamma_i=\{\gamma\}$ and $L_i=\{a^\dagger\}$. We also set $H=0$ since $T_Q$ should be purely dissipative. The equation of motion of $a$ reduces to
\begin{equation}
	\frac{d}{d t} a=\frac{\gamma}{2} a
\end{equation}
with solution $a(t)=e^{\frac{\gamma}{2} t} a = \sqrt{\lambda} a$, where we make the identification $\lambda=e^{\gamma t}$. 
In general, we find
\begin{equation}
	\frac{d}{d t} a^n (a^{\dagger})^m=\frac{\gamma}{2}(n+m)a^n (a^{\dagger})^m,
\end{equation}
meaning that this evolution realizes the stretching map in anti-normal ordering. That is, $(a^n (a^{\dagger})^m)(t)=e^{\frac{\gamma}{2} t (n+m)} a^n (a^{\dagger})^m = (\sqrt{\lambda})^{(n+m)} a^n (a^{\dagger})^m$.\footnote{Note that for the choice of $L_i=\{a\}$, we get the opposite behavior, characterized by
\begin{equation}
	\frac{d}{d t} (a^{\dagger})^n a^m=-\frac{\gamma}{2}(n+m)(a^{\dagger})^n a^m
\end{equation}
leading to shrinking ($\lambda\leq1$) of all observables taken in normal ordering.}

@@

\begin{figure}[h]
    \centering
\begin{tikzpicture}
\begin{axis}[
height=7cm,
width=\linewidth*0.8,
grid=both,
grid style={line width=.1pt, draw=gray!25},
axis lines=middle,
xlabel = \(\Sigma\),
ylabel = \(S\),
legend style={at={(0.95,0.65)},anchor=east},
]
\addplot[thick,blue,samples=150,domain=0.01:1.5] {ln(x)+1};
\addlegendentry{\(\text{classical}\)}
\addplot[thick,BrickRed,densely dotted,samples=150,domain=0.5:1.5] {(x+1/2)*ln(x+1/2)-(x-1/2)*ln(x-1/2)};
\addlegendentry{\(\text{quantum}\)}
\addplot[thick,ForestGreen,dashed,samples=150,domain=0.25:1.5] {((2*x+1/2)*ln(2*x+1/2)-(2*x-1/2)*ln(2*x-1/2) - ln(2)};
\addlegendentry{\(\text{$\lambda = 2$}\)}
\addplot[thick,violet,densely dashed,samples=150,domain=0.05:1.5] {((10*x+1/2)*ln(10*x+1/2)-(10*x-1/2)*ln(10*x-1/2) - ln(10)};
\addlegendentry{\(\text{$\lambda = 10$}\)}
\end{axis}
\end{tikzpicture}
    \caption{Entropy $S$ in nats for a Gaussian state as a function of uncertainty $\Sigma$, measured in units of $\hbar$. Between the classical and the quantum case, we have the quantum case where pure states are rescaled by a factor of $\lambda$: $S_{\lambda Q}(\Sigma) = S_Q(\lambda \Sigma) - \ln(\lambda)$. Taking $\lambda$ to infinity corresponds to taking $\hbar$ to zero.}
    \label{fig:uncertainty_scaled}
\end{figure}

As a more quantitative illustration, we can see what happens to the entropy of Gaussian states as we reduce the lowest possible uncertainty in the redefined quantum space. The entropy will become $S_{\lambda Q}(\Sigma) = S_Q(\lambda \Sigma) - \ln(\lambda)$. As we can see in Fig.~\ref{fig:uncertainty_scaled}, even with low factors of $\lambda$ the entropy curve approaches the classical one. If one takes the limit $\lambda \to \infty$, the above expression reduces to the classical equation.

Note that the above argument works for any map $T_Q \circ U$ that combines the pure stretching map with an arbitrary unitary evolution $U$. Also, while we have not shown that anti-normal ordering is the only ordering that allows a stretching map, it will need to have the same effect on $X$ and $P$, leading to the same limit. The question of whether all maps that perform the same group contraction can be expressed as $T_Q \circ U$ remains open. However, they will factorize in that fashion in the limit, since the classical limit can always be factorized as a pure stretching map following a symplectomorphism. Similarly, the question of whether $T_Q$ increases the entropy of all states by the same amount remains open. However, it will do so in the limit since $T_Q$ will become closer and closer to a pure classical stretching map. Lastly, we have not shown that all transformations that increase entropy must stretch phase space. Note, however, that a finite region of phase space can only hold mixed states with finite entropy. Therefore a map that does not stretch some region of phase space will necessarily lead to states whose entropy will not go to infinity as the map is reapplied over and over. Regardless, our ultimate goal is not to study all possible ways entropy can be increased. Our goal is simply to show that, as entropy increases, the classical description becomes a suitable approximation.

@@

We have thus shown that, in the limit of high entropy, the Wigner distribution can be approximated by a positive function. We now need to show that the evolution can be approximated by classical Hamiltonian evolution. An intuitive way to understand why this works is to look at the evolution of the Wigner function under a Hamiltonian $H = p^2/2m + V$ where the potentials $V$ are analytic. We have~\cite{hillery1984distribution}
\begin{equation}
\begin{aligned}
    \frac{d}{dt} W &= \{\{H, W\}\} \\
    &= \{H, W\} + \sum_n \frac{\hbar^{2n} (-1)^n}{(2n+1)! \, 2^{2n}} \partial_x^{(2n+1)} V \partial_p^{(2n+1)} W.
\end{aligned}
\end{equation}
The evolution is in terms of the Moyal bracket $\{\{H,W\}\}$, which can be expanded in orders of $\hbar$ with the Poisson bracket $\{H,W\}$ as the leading term. In our limit, $\hbar$ is constant but as the function stretches all derivatives of $W$ decrease. Therefore the first term becomes dominant.

@@

The limit also gives us additional insights. As we saw, classical states for which $\Delta x \Delta p < \frac{\hbar}{e}$ are states with negative entropy, which imply a breakdown of thermodynamics. It is no wonder, then, electrons cannot fall on the nucleus or that classical mechanics gives us the wrong spectra for black-body radiation. Classical mechanics fails at low entropy. The use of the correspondence principle as guidance for the development of quantum mechanics, then, can be understood as requiring that the new quantized theory reproduces classical mechanics at high entropy.

>>>>

In both classical and quantum mechanics, Gaussian states maximize entropy for a single independent degree of freedom at a fixed uncertainty or, equivalently, minimize uncertainty at fixed entropy. This means that, if we fix the entropy $S$, we will have an uncertainty relationship~\cite{Carcassi:2022bpm}
\begin{equation}
    \sigma_x \sigma_p \geq \Sigma(S).
\end{equation}
where $\sigma_x$ and $\sigma_p$ are the standard deviations of position and momentum and $\Sigma$ is the determinant of the covariance matrix and. The specific value of the uncertainty $\Sigma$ will depend on the entropy and on whether we are using classical or quantum mechanics, though the relationship will always be saturated by Gaussian states with no correlation between $x$ and $p$.

@@

Mathematically, the trace distance $T(\rho,\sigma)$ between two mixed states $\rho$ and $\sigma$ is contractive under a completely positive trace-preserving (CPTP) map $M$. That is, $T(M(\rho),M(\sigma)) \leq T(\rho,\sigma)$~\cite{nielsen2010quantum}. In the finite-dimensional case, we can have a CPTP map that increases the entropy of all states except that of the maximally mixed state, which is a fixed point.\footnote{This is a particular instance of mixing/relaxing ergodic quantum channels where the fixed point is the maximally mixed state~\cite{Burgarth2012ErgodicAM}.}  Under such a map, all pure states are mapped to mixed states, orthogonal states are mapped to non-orthogonal states and the map is strictly contractive. Moreover, even if observable do not commute in general, they commute for the maximally mixed state $\rho = I/n$ in the following sense:
\begin{equation}
	\<AB\>_{\rho} = \tr(AB\rho) = \tr(ABI/n) = \tr(AB)/n = \tr(BA)/n = \tr(BAI/n)= \tr(BA\rho) = \<BA\>_{\rho}
\end{equation}
Observables for a state close enough to the maximally mixed state, then, will ``almost commute'' in the sense that the expectation of different permutations of their product will be small.

In section~\ref{sec:high_entropy_limit}, when we construct the high-entropy limit, the map that results will follow this intuition in the infinite-dimensional case, with the only difference that there is no maximally mixed state that does not change.\footnote{In the infinite-dimensional case, one could have infinite-dimensional subspaces that remain orthogonal while increasing the entropy of all its elements. This corresponds, for example, to the case where there are conserved quantities. Note that in the map we construct in section 4, the expectation of all polynomials of position and momentum changes, and therefore no function of position and momentum is a conserved quantity. }  If we call $\mathcal{G}$ the space of all mixtures of Gaussian states, the states with a non-negative Wigner function, given an arbitrary mixed state $\rho$, we will find a state $\sigma_{\rho} \in \mathcal{G}$ that is closest to $\rho$. As we apply our entropy-increasing map, the entropy of $\rho$ increases and $\sigma_{\rho}$ will get closer to $\rho$. In this sense the states will ``look classical.''

@@

The failure of classical statistical mechanics to predict the black-body radiation spectrum was one of the key drivers for the development of quantum theory. The spectrum predicted by classical mechanics is given by the Rayleigh–Jeans law,
\begin{equation}
    \frac{2 \nu^2 k_rext{B} T}{c^2} = \frac{2 \nu^2}{c^2 \beta},
\end{equation}
where $\beta = \frac{1}{k_\text{B} T}$. The one predicted by quantum mechanics is given by Planck's law,
\begin{equation}
    \frac{ 2 h \nu^3}{c^2} \frac 1{\exp\left(\frac{h\nu}{k_\mathrm B T}\right) - 1} = \frac{ 2 h \nu^3}{c^2} \frac 1{e^{h \beta \nu} - 1}.
\end{equation}
It is well known that the two agree for small values of $\nu$ since $e^x \simeq 1 + x + O(x^2)$ for $x\ll 1$.
\begin{equation}
    \frac{ 2 h \nu^3}{c^2} \frac 1{e^{h \beta \nu} - 1} = \frac{ 2 h \nu^3}{c^2} \frac 1{1 + h \beta \nu + O\left(\nu^2\right) - 1} \simeq \frac{2 \nu^2}{c^2 \beta}.
\end{equation}

@@

Having given qualitative reasons for the limit, and having seen how, in specific cases, standard arguments can be reinterpreted consistently with our view, we now develop the limit as a direct consequence of entropy increase. Since the maximum entropy attainable by a quantum system is the logarithm of the dimension of the corresponding Hilbert space~\cite{nielsen2010quantum}, the high-entropy limit exists only for infinite-dimensional spaces. This explains why spin, which lives in a finite-dimensional space, is an intrinsically quantum property. Therefore we are going to concentrate on the case of a single degree of freedom identified by position and momentum.\footnote{A similar limit should exist for an infinite-dimensional directional degree of freedom (i.e. for angular momentum). Though technically not a limit but more of an approximation, for finite-dimensional spaces one could look at mixed state that are close to the maximally mixed states (i.e. $\rho = I/n + \epsilon \sigma$).} The case of multiple degrees of freedom can be recovered by increasing the entropy of all DOFs at the same time, that is, by increasing the entropy of each DOF independently, without introducing correlations.

@@

For a pure stretching map, we can provide a more specific characterization. First of all, given that the map will act linearly on the space of probability distributions, once we characterize its action on distributions with compact support, we fully characterize the map. Furthermore, a distribution with compact support is always fully characterized by all its central moments, that is, the expectations for all polynomials of position and momentum (i.e. the moment problem is always solvable). Therefore, once we know how the central moments transform through the map, we know how all distributions with compact support transform and therefore we fully characterize the map. This means that $T$ is a pure stretching map if and only if
\begin{equation}
	\langle T(x^np^m) \rangle = (\sqrt{\lambda})^{(n+m)} \langle x^n p^m \rangle.
\end{equation}
Given the linearity of the expectation, this relationship will remain true for all distributions that have finite moments. In particular, this will be true for all Schwartz functions. Therefore, we can use the above as the defining property of the pure stretching map.

@@

If pure quantum stretching maps $T_Q$ exist, they must be CPTP maps as they must transform mixed states into mixed states. Moreover, since they have to increase entropy for all states, they must be describing an open quantum system. We thus show that pure stretching maps can be expressed as the solution of a master equation in Lindblad form and the Heisenberg picture. We start with
\begin{equation}
	\frac{d}{d t} X=\frac{i}{\hbar}[H,X]+\sum_i \gamma_i \left(L_i^\dagger X L_i-\frac{1}{2}\left\{L_i^\dagger L_i,X\right\}\right)
\end{equation}
where $X$ is an operator, $L_i$ are the jump operators and $\gamma_i$ are positive parameters. To define $T_Q$ for a single DOF we set $\gamma_i=\{\gamma\}$ and $L_i=\{a^\dagger\}$.\footnote{Since $a^{\dagger} |\psi\> = a^\dagger c_n |n\> = c_n \sqrt{n+1} |n+1\>$, $|\psi\>$ is in the domain of $a^\dagger$ if and only if $\sum |c_n|^2 n < \infty$ or, equivalently, the expectation $\<\psi|n|\psi\>$ is finite. Since every element of the basis $|n\>$ is in the domain, $a^\dagger$ is dense in $L^2$.} We also set $H=0$ since $T_Q$ should be purely dissipative. The equation of motion of $a$ reduces to
\begin{equation}
	\frac{d}{d t} a=\frac{\gamma}{2} a
\end{equation}
with solution $a(t)=e^{\frac{\gamma}{2} t} a = \sqrt{\lambda} a$, where we make the identification $\lambda=e^{\gamma t}$. 
In general, we find
\begin{equation}
	\frac{d}{d t} a^n (a^{\dagger})^m=\frac{\gamma}{2}(n+m)a^n (a^{\dagger})^m,
\end{equation}
meaning that this evolution realizes the stretching map in anti-normal ordering. That is, $(a^n (a^{\dagger})^m)(t)=e^{\frac{\gamma}{2} t (n+m)} a^n (a^{\dagger})^m = (\sqrt{\lambda})^{(n+m)} a^n (a^{\dagger})^m$.\footnote{Note that for the choice of $L_i=\{a\}$, we get the opposite behavior, characterized by
\begin{equation}
	\frac{d}{d t} (a^{\dagger})^n a^m=-\frac{\gamma}{2}(n+m)(a^{\dagger})^n a^m
\end{equation}
leading to shrinking ($\lambda\leq1$) of all observables taken in normal ordering.}

@@

\begin{figure}[h]
    \centering
\begin{tikzpicture}
\begin{axis}[
height=7cm,
width=\linewidth*0.8,
grid=both,
grid style={line width=.1pt, draw=gray!25},
axis lines=middle,
xmin=0,
xlabel = \(\Sigma\),
ylabel = \(S\),
legend style={at={(0.95,0.25)},anchor=east},
]
\addplot[thick,blue,samples=150,domain=0.06:1.5] {ln(x)+1};
\addlegendentry{\(\text{classical}\)}
\addplot[thick,BrickRed,densely dotted,samples=150,domain=0.5:1.5] {(x+1/2)*ln(x+1/2)-(x-1/2)*ln(x-1/2)};
\addlegendentry{\(\text{quantum}\)}
\addplot[thick,ForestGreen,dashed,samples=150,domain=0.25:1.5] {((2*x+1/2)*ln(2*x+1/2)-(2*x-1/2)*ln(2*x-1/2) - ln(2)};
\addlegendentry{\(\text{$\lambda = 2$}\)}
\addplot[thick,violet,densely dashed,samples=150,domain=0.05:1.5] {((5*x+1/2)*ln(5*x+1/2)-(5*x-1/2)*ln(5*x-1/2) - ln(5)};
\addlegendentry{\(\text{$\lambda = 5$}\)}
\end{axis}
\end{tikzpicture}
    \caption{Entropy $S$ in nats for a Gaussian state as a function of uncertainty $\Sigma$, measured in units of $\hbar$. It shows the effect of the transition from classical to quantum by shrinking the pure states by a factor of $\lambda$ instead of stretching the mixed states by the same factor. The rescaled uncertainty for pure states becomes $\hbar/\lambda$ and the modified Gaussian bound as becomes $S_{\lambda Q}(\Sigma) = S_Q(\lambda \Sigma) - \ln(\lambda)$. Taking $\lambda$ to infinity corresponds to taking $\hbar/\lambda$ to zero.}
    \label{fig:uncertainty_scaled}
\end{figure}

As a more quantitative illustration, we can see what happens to the entropy of Gaussian states as we reduce the lowest possible uncertainty in the redefined quantum space. The entropy will become $S_{\lambda Q}(\Sigma) = S_Q(\lambda \Sigma) - \ln(\lambda)$. As we can see in Fig.~\ref{fig:uncertainty_scaled}, even with low factors of $\lambda$ the entropy curve approaches the classical one. If one takes the limit $\lambda \to \infty$, the above expression reduces to the classical equation. It should be stressed that these negative entropy states are fictitious, and it is only the difference in entropy that remains physically significant.

Note that the above argument works for any map $T_Q \circ U$ that combines the pure stretching map with an arbitrary unitary evolution $U$. Also, while we have not shown that anti-normal ordering is the only ordering that allows a stretching map, it will need to have the same effect on $X$ and $P$, leading to the same limit. The question of whether all maps that perform the same group contraction can be expressed as $T_Q \circ U$ remains open. However, they will factorize in that fashion in the limit, since the classical limit can always be factorized as a pure stretching map following a symplectomorphism. Similarly, the question of whether $T_Q$ increases the entropy of all states by the same amount remains open. However, it will do so in the limit since $T_Q$ will become closer and closer to a pure classical stretching map. Furthermore, we have not shown that all transformations that increase entropy must stretch phase space. Note, however, that a finite region of phase space can only hold mixed states with finite entropy. Therefore a map that does not stretch some region of phase space will necessarily lead to states whose entropy will not go to infinity as the map is reapplied over and over. Lastly, there is the question of whether any quantum channel that increases entropy will yield the classical limit. If by classical limit we mean the group contraction, then the only way to achieve it is through the rescaling of the commutator between $X$ and $P$, which is exactly a stretching map as we defined it. More in general, however, once a state has achieved sufficiently high entropy to be approximated by a classical state, it does not matter what process was used to achieve that high-entropy state. The remaining difficulty will be whether the evolution can still be approximated by a Hamiltonian evolution, which is likely to fail for a generic entropy-increasing process.\footnote{In the case that a process increases entropy differently in different regions of phase space, the evolution in the limit cannot be Hamiltonian, but may still be, for example, Newtonian.} Studying this more general case is outside of the scope of this work. Our goal is simply to show that, as entropy increases, the classical description becomes a suitable approximation.

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.4\textwidth]{stretchedCat.png}
	\caption{A cat state stretched with different values of $\lambda$. The axes are stretched by $\sqrt{\lambda}$ as well. The color scale is reduced to match the range of the function, though white always corresponds to zero. While the positive and negative peaks have comparable magnitude initially, the stretching map dampens the negative peak much more quickly. Note that, consistently with Fig. \ref{fig:uncertainty_scaled}, the negative values are severely dampened with $\lambda=5$.}
	\label{fig:cat_streatched}
\end{figure}

We have thus shown that, in the limit of high entropy, the Wigner distribution can be approximated by a positive function. We now need to show that the evolution can be approximated by classical Hamiltonian evolution. An intuitive way to understand why this works is to look at the evolution of the Wigner function under a Hamiltonian $H = p^2/2m + V$ where the potential $V$ is analytic. We have~\cite{hillery1984distribution}
\begin{equation}
\begin{aligned}
    \frac{d}{dt} W &= \{\{H, W\}\} \\
    &= \{H, W\} + \sum_n \frac{\hbar^{2n} (-1)^n}{(2n+1)! \, 2^{2n}} \partial_x^{(2n+1)} V \partial_p^{(2n+1)} W.
\end{aligned}
\end{equation}
The evolution is in terms of the Moyal bracket $\{\{H,W\}\}$, which can be expanded in orders of $\hbar$ with the Poisson bracket $\{H,W\}$ as the leading term. In our limit, $\hbar$ is constant but as the function stretches all derivatives of $W$ decrease. Therefore the first term becomes dominant.

It should be clear that this investigation does not exhaust all possible insights and links to the now vast literature on open quantum systems, quantum statistical mechanics, quantum information, quantum sensing and so on. For example, entropy and entropy increase play a role in several approaches: coarse graining(\href{https://journals.aps.org/prl/abstract/10.1103/PhysRevLett.99.180403}{CITE}), decoherence(CITE), stochastic processes (CITE \href{https://journals.aps.org/prl/abstract/10.1103/PhysRevLett.129.050401}{Quantum Fokker-Planck Master Equation for Continuous Feedback Control}) and information theoretical approaches to name a few. On a more technical level, since both the Husimi Q and the Wigner function converge to the classical distribution, the Wehrl entropy, which is the Shannon entropy calculated on the Husimi Q, will converge to the Gibbs entropy. One may ask, then, whether a high Wehrl entropy is already an indicator of classicality, and, if so, it would give another insight as to why the anti-normal ordering is important. Lastly, the role of entropic ideas is well established in historic literature. It would not be possible here to comment on all of them, and the more we mention, the more the omitted mentions are felt. Therefore we had to only explore the most important elements to establish the limit mathematically and under the smallest conceptual footprint, also as to not distract from the main point of the paper.

@@

The limit also gives us additional insights. As we saw, classical states for which $\sigma_x \sigma_p < \frac{\hbar}{e}$ are states with negative entropy, which imply a breakdown of thermodynamics. It is no wonder, then, electrons cannot fall on the nucleus or that classical mechanics gives us the wrong spectra for black-body radiation. Classical mechanics fails at low entropy. The use of the correspondence principle as guidance for the development of quantum mechanics, then, can be understood as requiring that the new quantized theory reproduces classical mechanics at high entropy.
